---
title: "Amazon Customer Review"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Amazon Customer Review}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

1.  The code dplyr verbs input and output data frames. This contrasts with base 
    R functions which more frequently work with individual vectors.

1.  dplyr relies heavily on "non-standard evaluation" so that you don't need to 
    use `$` to refer to columns in the "current" data frame. This behaviour 
    is inspired by the base functions `subset()` and `transform()`.
    
1.  dplyr solutions tend to use a variety of single purpose verbs, while base 
    R solutions typically tend to use `[` in a variety of ways, depending on the 
    task at hand. 
    
1.  Multiple dplyr verbs are often strung together into a pipeline by `%>%`.
    In base R, you'll typically save intermediate results to a variable that
    you either discard, or repeatedly overwrite.

1.  All dplyr verbs handle "grouped" data frames so that the code to perform a
    computation per-group looks very similar to code that works on a whole 
    data frame. In base R, per-group operations tend to have varied forms.
    
    
    
  # One table verbs

The following table shows a condensed translation between dplyr verbs and their base R equivalents. The following sections describe each operation in more detail. You learn more about the dplyr verbs in their documentation and in For more `vignette("one-table")`.

| dplyr                          | base                                             |
|------------------------------- |--------------------------------------------------|
| `arrange(df, x)`               | `df[order(x), , drop = FALSE]`                   | 
| `distinct(df, x)`              | `df[!duplicated(x), , drop = FALSE]`, `unique()` | 
| `filter(df, x)`                | `df[which(x), , drop = FALSE]`, `subset()`       | 
| `mutate(df, z = x + y)`        | `df$z <- df$x + df$y`, `transform()`             | 
| `pull(df, 1)`                  | `df[[1]]`                                        | 
| `pull(df, x)`                  | `df$x`                                           | 
| `rename(df, y = x)`            | `names(df)[names(df) == "x"] <- "y"`             | 
| `relocate(df, y)`              | `df[union("y", names(df))]`                      | 
| `select(df, x, y)`             | `df[c("x", "y")]`, `subset()`                    | 
| `select(df, starts_with("x"))` | `df[grepl("^x", names(df))]`                     | 
| `summarise(df, mean(x))`       | `mean(df$x)`, `tapply()`, `aggregate()`, `by()`  | 
| `slice(df, c(1, 2, 5))`        | `df[c(1, 2, 5), , drop = FALSE]`                 | 






```{r setup}
library(EmoReader)
```


Loading the data
```{r}
str(amazon_data)

```

```{r}
head(amazon_data)
```

